%%
%%% >>> Resume and Published papers
%%
\chapter{作者简历}

\section*{作者基本情况}

刘志聪，男，1992年出生于河北省邢台市平乡县，未婚，中国科学院高能物理研究所博士研究生。

\section*{教育情况}

2009年9月到2013年7月，天津大学，本科。

专业：应用物理学。

2013年9月到2018年7月，中国科学院高能物理研究所，博士研究生。

专业：粒子物理与原子核物理，专业方向：加速器物理。

\section*{联系方式}

通讯地址：北京市石景山区玉泉路19号（乙）918信箱，中国科学院高能物理研究所

邮编：100049

E-mail: liuzhicong@ihep.ac.cn

\chapter{攻读学位期间发表的学术论文及科研成果}
\begin{enumerate}
  \item \textbf{\textit{Liu, Z.}}, Qiang J. Symplectic Multi-Particle Tracking Using GPU. Computer Physics Communications. Under review.
  \item Li Chao, \textbf{\textit{Liu Zhicong}}, Zhao Yaliang, Qin Qing, Nonlinear resonance and envelope instability of intense beam in axial symmetric periodic channel. Nuclear Instruments and Methods in Physics Research Section A: Accelerators, Spectrometers, Detectors and Associated Equipment, 813, 13-18.
  \item \textbf{\textit{Liu, Z.}}, Li, C., Qin, Q., Zhao, Y., \& Yan, F. Beam Dynamics Study of C-Ads Injector-I With Developing P-Topo Code. In 57th ICFA Advanced Beam Dynamics Workshop on High-Intensity and High-Brightness Hadron Beams (HB'16), Malmö, Sweden, July 3-8, 2016 (pp. 195-198).
  \item \textbf{\textit{Liu, Z.}}, Qiang, J. Symplectic Multi-Particle Tracking Using Cuda. In 8th Int. Particle Accelerator Conf.(IPAC'17), Copenhagen, Denmark, 14-19 May, 2017 (pp. 3756-3759).
  \item Yu, C., Duan, Z., Gu, S., Guo, Y., Huang, X., Ji, D., Ji H., Jiao Y.,\textbf{\textit{ Z Liu}} ... \& Qin, Q. (2016, June). BEPCII performance and beam dynamics studies on luminosity. IPAC16, Busan, Korea, May 8-13, 2016 (pp. 1014-1018).
\end{enumerate}













\section*{项目资助情况}

%%可以随意添加新的条目或是结构

%%
%%% >>> Acknowledgements
%%
\chapter{致\quad 谢}

值此论文完成之际，谨在此向多年来给予我关心和帮助的老师、学长、同学、
朋友和家人表示衷心的感谢！
